LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-10-21 main.tex
Reword conclusions section

LCS Tool leverages the capabilities of MATLAB extensively. For FTLE based extraction of LCSs, computational performance has received considerable attention \citep{conti12:_gpu_apu_finit_time_lyapun_expon,miron12:_anisot_lagran_coher_struc}. We hope to see similar computational advances for the publicly available LCS Tool platform. Optimizing computational performance will likely aid the application of variational LCS methods to large-scale real-time forecasting applications, such as the tracking of environmental contaminants\citep{olascoaga12:_forec}.

We also hope that LCS Tool will serve as a foundation for the numerical
implementation of recent theoretical advances. These include the geodesic theory of parabolic LCSs (jet cores)\citep{farazmand14:_shearless} and the variational theory of hyperbolic and elliptic LCSs for three-dimensional
flows\citep{blazevski14:_hyper_ellip_trans_barrier_three}.

>>>>

LCS Tool leverages the capabilities of MATLAB. For FTLE based extraction of LCSs, computational performance has received considerable attention \citep{conti12:_gpu_apu_finit_time_lyapun_expon,miron12:_anisot_lagran_coher_struc}.
We think LCS Tool can facilitate similar computational advances for variational LCS methods.
Optimizing computational performance will aid applications to large-scale forecasting applications, such as the tracking of environmental contaminants\citep{olascoaga12:_forec}.

We hope LCS Tool will serve as a foundation for the numerical implementation of recent theoretical advances.
These include the geodesic theory of parabolic LCSs (jet cores)\citep{farazmand14:_shearless} and the variational theory of hyperbolic and elliptic LCSs for three-dimensional flows\citep{blazevski14:_hyper_ellip_trans_barrier_three}.
